---
title: "Pilot Planning"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pilot Planning}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows the pilot-planning helpers motivated by Appendix E. These
functions are screening tools: they identify pilot sizes that pass necessary
conditions for assignment adaptation to be worthwhile, before any pilot data
are observed.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(cmrdesign)
```

## Planning inputs

Suppose the total experimental budget is 3,000 observations. Historical data or
a closely related study suggest that the treatment-arm standard deviation is
about 0.18 and the control-arm standard deviation is about 0.28 on the
`[0, 1]` outcome scale.

```{r inputs}
n_total <- 3000
sigma1 <- 0.18
sigma0 <- 0.28
alpha <- 0.05
```

## Break-even pilot share

The break-even share is based on the amount of variance imbalance available for
CMR to exploit.

```{r break-even}
break_even_pilot_share(sigma1, sigma0)
n_total * break_even_pilot_share(sigma1, sigma0)
```

If the two standard deviations are nearly identical, the break-even share is
near zero and a positive pilot is hard to justify on assignment-design grounds.

## Activation thresholds

For bounded outcomes, very small pilots may not move the confidence rectangle
away from the full `[0, 0.25]` variance range. The activation threshold is the
smallest even total pilot size that clears this screen.

```{r activation}
activation_threshold_bounded(alpha = alpha, max_total_pilot = n_total - 2)
activation_threshold_bernoulli(alpha = alpha)
```

Binary outcomes have a separate exact-Bernoulli activation screen.

## Viability band

The viability band combines the activation screen with the break-even cap.

```{r viability-band}
band <- pilot_viability_band(
  n = n_total,
  sigma1 = sigma1,
  sigma0 = sigma0,
  alpha = alpha,
  method = "bounded"
)

band$nonempty
band$min_feasible
band$max_feasible
length(band$feasible_pilot_sizes)
```

The returned object keeps the full admissible even grid for audit.

```{r feasible-grid}
head(band$feasible_pilot_sizes)
tail(band$feasible_pilot_sizes)
```

## Check a desired pilot size

`cmr_plan()` reports whether a proposed pilot size lies inside the necessary
viability band and gives the package's default suggestion.

```{r desired-pilot}
plan <- cmr_plan(
  n = n_total,
  sigma1 = sigma1,
  sigma0 = sigma0,
  alpha = alpha,
  method = "bounded",
  desired_pilot = 120
)

plan$suggested_pilot
plan$desired_status
plan$recommendation
plan$caveat
```

The same calculation can be run with variance inputs instead of standard
deviation inputs.

```{r variance-inputs}
plan_from_variances <- cmr_plan(
  n = n_total,
  sigma1 = sigma1^2,
  sigma0 = sigma0^2,
  input = "variance",
  alpha = alpha,
  method = "bounded",
  desired_pilot = 120
)

plan_from_variances$desired_status
plan_from_variances$suggested_pilot
```

For applications where all observations are eventually pooled into the final
analysis, use `accounting = "pooled"` to omit the design-only break-even cap.

```{r pooled-accounting}
pooled_plan <- cmr_plan(
  n = n_total,
  sigma1 = sigma1,
  sigma0 = sigma0,
  alpha = alpha,
  method = "bounded",
  accounting = "pooled",
  desired_pilot = 400
)

pooled_plan$desired_status
pooled_plan$band$min_feasible
pooled_plan$band$max_feasible
```
